Plant-pollintor networks worldwide are composed by the same specific building blocks

### 2021-05-18 Draft/Draft.Rmd
I think I did what I wanted to do. Not clean.

plant_position_percentiles_filtered <- all_position_percentiles %>% 
  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
         !is.na(expected_freq_its_GF)) #ME DA ERROR
pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
         !is.na(expected_freq_its_GF))

@@

# Mean percentile and SE taking into account the study system
plant_codes <- plant_position_percentiles_filtered$position %>% unique()
plant_means <- tibble(position = plant_codes)
plant_means$mean <- NA
plant_means$SE <- NA

for(i.pos in 1:length(plant_codes)){

  m <- lmer(percentil_its_GF ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
            data = subset(plant_position_percentiles_filtered,
                          position == plant_codes[i.pos]))

  plant_means$mean[i.pos] <- fixed.effects(m) %>% unname()
  plant_means$SE[i.pos] <- sqrt(diag(vcov(m)))

@@

GF_plant_pos <- ggplot(NULL) + 
  geom_point(data = plant_position_percentiles_filtered,
             aes(x=as.factor(position), y=percentil_its_GF, 
                 color = as.factor(position)),
             position = "jitter",alpha=0.5)+
  facet_wrap(~Node_FG,ncol = 5)+
  geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
             size=2)+
  labs(x="Position", y = "Percentile",title = "Plants")+
  theme_bw()+
  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
  coord_flip()

# Pollinators--------

>>>>

plant_position_percentiles_filtered <- all_position_percentiles %>% 
  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
         !is.na(expected_freq_its_GF)) 
pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
         !is.na(expected_freq_its_GF))

@@

# Mean percentile and SE taking into account the study system
combinations <- paste(plant_position_percentiles_filtered$position,
                           plant_position_percentiles_filtered$Node_FG, sep = "_")
combinations_codes <- combinations %>% unique()
plant_means <- tibble(position = combinations_codes)
plant_codes <- plant_position_percentiles_filtered$position %>% unique()
#plant_means <- tibble(position = plant_codes)
plant_means$mean <- NA
plant_means$SE <- NA

j <-  1
for(i.pos in 1:length(plant_codes)){

  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), 
            data = subset(plant_position_percentiles_filtered,
                          position == plant_codes[i.pos]))  
  #summary(m)
  temp <- fixed.effects(m) %>% unname()
  plant_means$mean[c(j:(j+4))] <- c(temp[1], #to get real means per FG
                                    temp[1]+temp[2],
                                    temp[1]+temp[3],
                                    temp[1]+temp[4],
                                    temp[1]+temp[5])
  temp <- sqrt(diag(vcov(m)))
  plant_means$SE[c(j:(j+4))] <- c(temp[1], 
                                    temp[1]+temp[2],
                                    temp[1]+temp[3],
                                    temp[1]+temp[4],
                                    temp[1]+temp[5]) #Alfonso, los errores se suman tambien??
  j <- j+5 #esto puede que sea una guarrada

@@

#NO SE PLOTEAR ESTO... 
plant_means$true_position <- seq(1,220, 2)
plant_means$FG <- seq(1,220, 2)
plant_means$true_position <- unlist(strsplit(plant_means$position, "_", TRUE))[seq(1,220, 2)]
plant_means$FG <- unlist(strsplit(plant_means$position, "_", TRUE))[seq(2,220, 2)]

GF_plant_pos <- ggplot(NULL) + 
  #geom_point(data = plant_means, #AQUI NO SE PONER LOS PUNTITOS :(
             #aes(x=as.factor(position), y=percentil_its_GF, 
              #   color = as.factor(position)),
             #position = "jitter",alpha=0.5)+
  facet_wrap(~FG)+
  geom_errorbar(data = plant_means,aes(x = as.factor(true_position), ymin=mean-SE, ymax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = plant_means,aes(x = as.factor(true_position), y=mean), 
             size=2)+
  labs(x="Position", y = "Percentile",title = "Plants")+
  theme_bw()+
  #theme(legend.position = "none",axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
  coord_flip()

GF_plant_pos #vaya kk de plot

#mejor para comparar por posiciones?
GF_plant_pos2 <- ggplot(NULL) + 
  facet_wrap(~true_position)+
  geom_errorbar(data = plant_means,aes(x = as.factor(FG), ymin=mean-SE, ymax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = plant_means,aes(x = as.factor(FG), y=mean), 
             size=2)+
  labs(x="FG", y = "Percentile",title = "Plants")+
  theme_bw()+
  #theme(legend.position = "none",axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
  coord_flip()

GF_plant_pos2 #creo que mejor... me sigue sorprendiendo el e.g. GF 4. que esta asociado con muchas posiciones...

# Pollinators-------- NOT UPDATED
